Assignment 2

### 2025-02-28 code/Reddit_API.qmd
adding API code

```{r}
test <- topic_urls |> 
  # create date string to date object
  mutate(date_utc = ymd(date_utc),
         text = na_if(text, "") ) |> 
  # if text is NA, it's a picture or video, drop it 
  filter(!is.na(text),
         date_utc > "2024-11-05", ,
         !str_starts(text, "https")
         )
```

>>>>

    -   DOGEcoin is a cryptocurrency, and we need to filter out any posts that are unrelated to our topic of interest.

```{r}
test <- topic_urls |> 
  # create date string to date object
  mutate(date_utc = ymd(date_utc),
         text = na_if(text, "") ) |> 
  # if text is NA, it's a picture or video, drop it 
  filter(!is.na(text),
         date_utc > "2024-11-05", ,
         !str_starts(text, "https"),
         !str_detect(text, "crypto|coin")
         )
```
